Glyph-maps for Visualizing Climate Data and Models

### 2011-09-28 paper.tex
A bit more restructuring

@@

\section{What to plot: raw data, trend lines, residuals,  seasonal}

A generalized additive model \citep{wood:2006} with a seasonal term and a long-term smooth term can be useful. This is revealing for smooth models of surface temperature, shown in Figure~\ref{fig:scaling}. Each location is modeled using a generalized additive model \citep{wood:2006} with a seasonal term and a long-term smooth term. The three plots in the figure show the long-term smooth term. %Because some locations are uniformly warmer than others, the impact of changes across time are diminished. In the center plot, each location is scaled by dividing out the maximum, and on the right, each location is scaled to range $[0, 1]$. These emphasize individual changes but lose the ability to make global comparisons, and need caution when interpreting - a small absolute change gets blown up into a large relative change.
 %The three plots in the figure show the long-term smooth term. Because some locations are uniformly warmer than others, the impact of changes across time are diminished.

% is a extremely useful technique: product plots, ANOVA, ...  For glyph plots, it's often useful to partition the glyphs into shape and scale components, decomposing the values into a product of maximum and scaled values.  In this section we explore how decomposing each series into scale and shape components can be useful.

*** Need three plots here: trend, seasonality and residuals, shall we do this with NASA ozone data or stick to temperature?

Issues of scale relative to modeling. Switching from the data to model summaries brings new scaling issues. Often the scale of the raw data is ignored when the model is plotted, one usually shows just the line showing the trend, in the range of the trend. This has the effect of exaggerating the significance of the model. Scaling the trend lines relative to the range of the data may be useful sometimes.

\section{Regular vs irregular locations}~\label{sec:irregular}

>>>>

% \section{What to plot: raw data, trend lines, residuals,  seasonal}
% 
% A generalized additive model \citep{wood:2006} with a seasonal term and a long-term smooth term can be useful. This is revealing for smooth models of surface temperature, shown in Figure~\ref{fig:scaling}. Each location is modeled using a generalized additive model \citep{wood:2006} with a seasonal term and a long-term smooth term. The three plots in the figure show the long-term smooth term. 
% 
% %Because some locations are uniformly warmer than others, the impact of
% %changes across time are diminished. In the center plot, each location is
% %scaled by dividing out the maximum, and on the right, each location is scaled
% %to range $[0, 1]$. These emphasize individual changes but lose the ability to
% %make global comparisons, and need caution when interpreting - a small
% %absolute change gets blown up into a large relative change.
% 
% *** Need three plots here: trend, seasonality and residuals, shall we do this with NASA ozone data or stick to temperature?
% 
% Issues of scale relative to modeling. Switching from the data to model summaries brings new scaling issues. Often the scale of the raw data is ignored when the model is plotted, one usually shows just the line showing the trend, in the range of the trend. This has the effect of exaggerating the significance of the model. Scaling the trend lines relative to the range of the data may be useful sometimes.

@@

\section{Non-gridded data}~\label{sec:irregular}
